Updates on the Exoplanet Orbit Database

### 2014-03-06 draft/ms.tex
Add several missing references in Sec 2.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the EOD}\label{sec:update}
ZZZ make sure to cite Wright and Gaudi paper for the definition of orbital elements.

@@

%------------------------------------------------------------------------------
\subsection{Secondary Eclipse}
We have added an entirely new set of fields for the secondary eclipse. Previously, due to the limits of instrumentation, there were not much available measured secondary eclipse depths. Since \cite{Wright2011}, as many different surveys have been launched, secondary eclipse depths at multiple bands are now available. Therefore, we added this entire new set of fields since.

{\bf SE} flag indicates whether the system has detected secondary eclipse in any of the two Micron All-Sky Survey (2MASS) $J$, $H$, and $K_s$, Kepler photometry band, and 4 Spitzer IRAC bands. SE is a boolean and being true indicates the system has at least one detected secondary eclipse. 
ZZZ add 2MASS reference!

@@

%------------------------------------------------------------------------------
\subsection{Coordinates and Catalogs}
We report the coordinates of the host star as well as the stellar ID as designated by different catalogs. 
We added {\bf DIST} since \cite{Wright2011}, which is the distance of the host star in the unit of pc. If only parallax (PAR) is given, we convert it to DIST and vice versa. If the literature does not report DIST or PAR, then we obtain PAR from the Hipparcos data set by van Leeuwen (2009). ZZZ add a reference for Leeuwen

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the EOD}\label{sec:update}
Make sure to cite \cite{Wright2013} for the definition of orbital elements.

@@

%------------------------------------------------------------------------------
\subsection{Secondary Eclipse}

We have added an entirely new set of fields for the secondary
eclipse. Previously, due to the limits of instrumentation, there were
not much available measured secondary eclipse depths. Since
\cite{Wright2011}, as many different surveys have been launched,
secondary eclipse depths at multiple bands are now
available. Therefore, we added this entire new set of fields since.

{\bf SE} flag indicates whether the system has detected secondary
eclipse in any of the two Micron All-Sky Survey (2MASS;
\citealt{Skrustskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
and 4 Spitzer IRAC bands. SE is a boolean and being true indicates the
system has at least one detected secondary eclipse.

@@

%------------------------------------------------------------------------------
\subsection{Coordinates and Catalogs}
We report the coordinates of the host star as well as the stellar ID
as designated by different catalogs.  We added {\bf DIST} since
\cite{Wright2011}, which is the distance of the host star in the unit
of pc. If only parallax (PAR) is given, we convert it to DIST and vice
versa. If the literature does not report DIST or PAR, then we obtain
PAR from the Hipparcos data set by \cite{van Leeuwen2009}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
